---
title: "Multipage Tables"
output: pagedown::html_paged
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      error = FALSE)
```

```{r}
library(tidyverse)
library(flextable)
```

Here's some fake data.

```{r}
fake_data <- tibble(
  year = seq(2000, 2020, 1),
  long_text = "Laborum proident sit anim duis culpa elit est aliquip culpa aliquip."
) %>% 
  mutate(row_number = row_number())
```

If I make a table from it, it flows across multiple pages and the formatting gets messed up.

```{r}
fake_data %>% 
  flextable()
```


Let's make a function to show just a portion of the data in a table at a time. 

```{r}
filtered_table <- function(start_row) {
  
  fake_data %>% 
    filter(between(row_number, start_row, start_row + 10)) %>% 
    flextable()
  
}
```

I can use this function to make a table with 11 rows.

```{r}
filtered_table(1)
```

But what I really want to do is have the code chunk generate two (or more) tables. I tried doing it with the code below, but no dice. It doesn't show anything when rendered.

```{r}
start_rows <- c(1, 11)

walk(start_rows, filtered_table)
```

